### 2024-06-16 basic-statistics.qmd
20240616 - clarification

- Cohen's $d$
- Standardized regression coefficient ($\beta$)
- Correlation coefficient ($r$)
- Coefficient of determination ($R^2$)
- Eta squared ($\eta^2$)
- Partial eta squared ($\eta_p^2$)

>>>>

- Cohen's $d$
- Standardized regression coefficient (beta; $\beta$)
- Correlation coefficient ($r$)
- Coefficient of determination ($R^2$)
- Eta squared ($\eta^2$)
- Partial eta squared ($\eta_p^2$)
